---
title: "M2 Thesis Perception - Minus Below Chance"
author:
  name: Erik Morris
  affiliation: Université Paris Cité
date: "May 28, 2024"
output:
  html_notebook:
    highlight: pygments
    number_sections: yes
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
      fig_crop: no
  html_document:
    toc: yes
    toc_depth: '6'
    df_print: paged
editor_options:
  markdown:
    wrap: sentence
---

# Load Packages

```{r message=FALSE}
loadPackage <- c('tidyverse', 'vroom', 'emmeans', 'lmerTest', 'lme4', 'Matrix', 'knitr', 'xtable', 'corrplot', 'kableExtra', 'broom.mixed', 'patchwork', 'ragg')
for(a in loadPackage){
  library(a, character.only = TRUE)
}
```

# Load Data

```{r}
# Read the cleaned OpenSesame output
dfMasterRaw.chance <- read.csv("Master_Reaction.csv", header = TRUE)
```


## Filter and Convert to Factors

```{r}
# Filter out the time-out responses by finding response = none or response_time = 3000
dfMaster.chance <- dfMasterRaw.chance %>% filter(response != "None", !Participant %in% c("FF05","FF10","FF20","FM01","FM06")) %>% select(-Condition)

## With Condition as a seven level factor combining Conditions and Dialect
dfMaster.chance <- dfMaster.chance %>% 
  mutate(Condition = case_when(grepl("1a_", experiment_file) ~ "1-Athens",
                               grepl("1b_", experiment_file) ~ "1-Thessaloniki",
                               grepl("1c_", experiment_file) ~ "1-Crete",
                               grepl("2a_", experiment_file) ~ "2-Athens",
                               grepl("2b_", experiment_file) ~ "2-Thessaloniki",
                               grepl("2c_", experiment_file) ~ "2-Crete",
                               TRUE ~ "3-All")
         )

# Convert the categorical variables to factors
dfMaster.chance <- dfMaster.chance %>%
  mutate(Dialect = factor(Dialect, labels = c("All", "Athens", "Thessaloniki", "Crete")),
         test_sp = factor(test_sp, labels = c("Multiple", "Single")),
         Block = factor(Block),
         correct = factor(correct),
         Condition = factor(Condition)
         )
```

## Add columns and Subset
```{r}
# Creating the contrast categories
dfMaster.chance <- dfMaster.chance %>%
  mutate(pair_type = case_when(Contrast %in% c(2,7,19) ~ "Native",
                               Contrast %in% c(4,5,6,10,11,12,14,17,20) ~ "Foreign",
                               Contrast %in% c(1,3,8,9,13,15,16,18,21) ~ "For-Nat",
                               TRUE ~ NA),
         obs_type = case_when(Contrast %in% c(1,2,3,7,8,9) ~ "Stop-Stop",
                              Contrast %in% c(4,5,6,10,11,12) ~ "Fric-Fric",
                              Contrast %in% c(13,14,15,16,17,18) ~ "Stop-Fric",
                              TRUE ~ NA)
         )

# Condition
dfByCond.chance <- dfMaster.chance %>% 
  group_by(Condition) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time))

# Block
dfByBlock.chance <- dfMaster.chance %>% 
  group_by(Block) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time))

# Dialect - Mostly for plots
dfByDialect.chance <- dfMaster.chance %>% 
  group_by(Dialect) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time)) 

# Test Block only
dfByTest.chance <- dfMaster.chance %>% 
  filter(Block==4) %>% 
  group_by(test_sp) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time))
```


# Plots
## Condition
```{r}
# Accuracy
dfByCond.chance %>% 
  ggplot(aes(x = mean_correct, y = Condition, fill = Condition)) + 
  theme_gray() +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) + 
  #coord_flip(ylim = c(50,100)) +
  coord_fixed(ratio = 3, xlim = c(50,100)) +
  labs(title = "Mean Accuracy by Condition",
       subtitle = "Excluding below chance",
       y = "Condition",
       x = "Mean Correct (%)") +
  geom_text(aes(label = round(mean_correct, digits = 2)),
            hjust = 1.25, 
            #vjust = 0.3,
            size = 3) +
  scale_fill_brewer(palette="Set2") + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        plot.margin = margin(t = 0, r = 0, b = 0.25, l = 0, unit = "cm"),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 2),
        axis.text = element_text(size = 10, colour = "black")) -> p.cond.a

# Reaction Time
dfByCond.chance %>% 
  ggplot(aes(x = reaction, y = Condition, fill = Condition)) + 
  theme_gray() +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) + 
  #coord_flip() +
  coord_fixed(ratio = 47, xlim = c(200,1000)) +
  labs(title = "Mean Response Time by Condition",
       subtitle = "Excluding below chance",
       caption = "Lower is better.",
       y = "Condition",
       x = "Mean Response Time (ms)") +
  geom_text(aes(label = round(reaction, digits = 2)),
            hjust = 1.25, 
            #vjust = 0.3,
            size = 3) +
  scale_fill_brewer(palette="Set2") + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 2),
        axis.text = element_text(size = 10, colour = "black")) -> p.cond.b
```

## Dialect
```{r}
# Accuracy
dfByDialect.chance %>% 
  ggplot(aes(x = Dialect, y = mean_correct, fill = Dialect)) + 
  theme_bw() +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) + 
  coord_cartesian(ylim = c(50,100)) +
  labs(title = "Mean Accuracy by Dialect",
       subtitle = "Excluding below chance",
       x = "Dialect",
       y = "Mean Correct (%)",
       tag = "A.") +
  geom_text(aes(label = round(mean_correct, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9),
            vjust=-0.25) +
  scale_fill_brewer(palette="Set2") + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 9, colour = "black")) -> p.dial.acc

# Reaction Time
dfByDialect.chance %>% 
  ggplot(aes(x = Dialect, y = reaction, fill = Dialect)) + 
  theme_bw() +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) + 
  coord_cartesian(ylim = c(400,800)) +
  labs(title = "Mean Response Time by Dialect",
       subtitle = "Excluding below chance",
       caption = "Lower is better",
       x = "Dialect", 
       y = "Mean Response Time (ms)") +
  geom_text(aes(label = round(reaction, digits = 2)), 
            size = 3,
            position=position_dodge(width=0.9), 
            vjust= -0.25) +
  scale_fill_brewer(palette="Set2") + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 2),
        axis.text = element_text(size = 9, colour = "black")) -> p.dial.rt
```

## Block
```{r}
# Accuracy
dfByBlock.chance %>% 
  ggplot(aes(x = Block, y = mean_correct, fill = Block)) + 
  theme_bw() +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) + 
  coord_cartesian(ylim = c(50,100)) +
  scale_x_discrete(labels = c("Practice", "1", "2", "3", "Test")) + 
  labs(title = "Mean Accuracy by Block",
       subtitle = "Excluding below chance",
       x = "Block", 
       y = "Mean Correct (%)",
       tag = "B.") +
  geom_text(aes(label = round(mean_correct, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9),
            vjust=-0.25) +
  scale_fill_brewer(palette="Set2") + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black")) -> p.block.acc

# Reaction Time
dfByBlock.chance %>% 
  ggplot(aes(x = Block, y = reaction, fill = Block)) + 
  theme_bw() +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) + 
  coord_cartesian(ylim = c(400,1000)) +
  scale_x_discrete(labels = c("Practice", "1", "2", "3", "Test")) + 
  labs(title = "Mean Response Time by Block",
       subtitle = "Excluding below chance",
       caption = "Lower is better",
       x = "Block", 
       y = "Mean Response Time (ms)") +
  geom_text(aes(label = round(reaction, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9), 
            vjust= -0.25) +
  scale_fill_brewer(palette="Set2") + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black")) -> p.block.rt
```

### With Condition breakdown
```{r}
# Regrouping to see Condition means per block for progression tracking
plot.line <- dfMaster.chance %>% 
  group_by(Block, Condition) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time)) %>% 
  filter(Block!=0)

# Renaming the lables so that Test is clear
block.labs <- c("1","2","3","Test")
names(block.labs) <- c(1,2,3,4)

plot.line %>%
  ggplot(aes(x = mean_correct, y = Condition, fill = Condition)) + 
  theme_bw() +
  geom_bar(stat = "identity", show.legend = FALSE) + 
  coord_fixed(ratio = 600/1, xlim = c(60,120)) + 
  labs(title = "Mean Accuracy by Block", 
       subtitle = "Excluding below chance",
       y = "Condition", 
       x = "Mean Correct (%)") +
  geom_text(aes(label = round(mean_correct, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9),
            hjust=-0.25) +
  scale_fill_brewer(palette="Set2") + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 8, colour = "black")) + 
  facet_grid(~Block, space = "free_x", labeller = labeller(Block = block.labs)) -> p.blcond
```

```{r}
# Saving the above plot
ggsave("plot_blcond.png", p.blcond, device = agg_png, width = 15,
       height = 6,
       units = "cm", res = 300, scaling = 0.9)
```


## Test Speaker
```{r}
# Accuracy
dfByTest.chance %>% 
  ggplot(aes(x = test_sp, y = mean_correct, fill = test_sp)) + 
  theme_bw() +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) + 
  coord_fixed(ratio = 1/30, ylim = c(50,100)) + 
  scale_x_discrete(labels = c("Multiple", "Single")) + 
  labs(title = "Test: Accuracy by Speaker",
       subtitle = "Average of all participants, excluding below chance",
       x = "Speaker",
       y = "Mean Correct (%)") +
  geom_text(aes(label = round(mean_correct, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9), 
            vjust=-0.25) + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 9, colour = "black")) -> p.test.acc

# Reaction Time
dfByTest.chance %>% 
  ggplot(aes(x = test_sp, y = reaction, fill = test_sp)) + 
  theme_bw() +
  geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) +
  coord_fixed(ratio = 1/300, ylim = c(400,850)) +
  scale_x_discrete(labels = c("Multiple", "Single")) + 
  labs(title = "Test: Response Time by Speaker",
       subtitle = "Average of all participants, excluding below chance",
       caption = "Lower is better",
       x = "Speaker",
       y = "Mean Response Time (ms)") +
  geom_text(aes(label = round(reaction, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9),
            vjust=-0.25) + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1.5),
        axis.text = element_text(size = 9, colour = "black")) -> p.test.rt
```


### By Dialect
```{r}
# Regrouping to see dialect scores in test block
dfMaster.chance %>% 
  filter(Block==4) %>% 
  group_by(test_sp, Dialect) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time)) -> dfByTestDialect.chance

# Accuracy
dfByTestDialect.chance %>%
  ggplot(aes(x = Dialect, y = mean_correct, fill = test_sp)) + 
  theme_bw() +
  geom_bar(stat = "identity", position = "dodge") + 
  coord_cartesian(ylim = c(0,100)) + 
  labs(title = "Test Block x Dialect: ", 
       subtitle = "Accuracy by Speaker No. across all Participants",
       x = "Dialect", 
       y = "Mean Correct (%)") + 
  scale_fill_discrete(name="Speaker", labels = c("Multiple", "Single")) +
  geom_text(aes(label = round(mean_correct, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9),
            vjust=-0.25) + 
  theme(plot.title = element_text(face = "bold", margin = margin(10,0,10,0), size = 14),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black"),
        legend.position = c(0.9,0.9), 
        legend.background = element_rect(fill = "transparent"),
        legend.key.size = unit(4, "mm"))# -> p.test.d.acc

# Reaction Times
dfByTestDialect.chance %>%
  ggplot(aes(x = Dialect, y = reaction, fill = test_sp)) +
  theme_bw() +
  geom_bar(stat = "identity", position = "dodge") + 
  labs(title = "Test Block x Dialect: ",
       subtitle = "Reaction Time by Speaker No. across all Participants",
       caption = "Lower is better",
       x = "Dialect",
       y = "Mean Reaction Time (ms)") + 
  scale_fill_discrete(name="Speaker", labels = c("Multiple", "Single")) +
  geom_text(aes(label = round(reaction, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9),
            vjust=-0.25) + 
  theme(plot.title = element_text(face = "bold", margin = margin(10,0,10,0), size = 14),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black"),
        legend.position = c(0.9,0.9), 
        legend.background = element_rect(fill = "transparent"),
        legend.key.size = unit(4, "mm"))# -> p.test.d.rt
```


### By Condition
```{r}
# Regrouping to see condition scores in test block
dfMaster.chance %>% 
  filter(Block==4) %>% 
  group_by(test_sp, Condition) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time)) -> dfByTestCondition.chance

# Accuracy
dfByTestCondition.chance %>%
  ggplot(aes(x = Condition, y = mean_correct, fill = test_sp)) + 
  theme_bw() +
  geom_bar(stat = "identity", position = "dodge") + 
  coord_fixed(ratio = 1/20, ylim = c(50,110)) + 
  labs(title = "Test x Condition: Accuracy by Speaker", 
       subtitle = "Average across all participants, excluding below chance",
       x = "Condition", 
       y = "Mean Correct Responses") + 
  scale_fill_discrete(name="Speaker", labels = c("Multiple", "Single")) +
  geom_text(aes(label = round(mean_correct, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9),
            vjust=-0.25) + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 8, colour = "black"),
        legend.position = c(0.9,0.9), 
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_text(size = 9),
        #legend.direction = "horizontal",
        legend.key.size = unit(4, "mm")) -> p.test.c.acc

# Reaction Time
dfByTestCondition.chance %>%
  ggplot(aes(x = Condition, y = reaction, fill = test_sp)) + 
  theme_bw() +
  geom_bar(stat = "identity", position = "dodge") + 
  coord_fixed(ratio = 1/300, ylim = c(200,1100)) +
  labs(title = "Test x Condition: Response Time by Speaker",
       subtitle = "Average across all participants, excluding below chance",
       caption = "Lower is better",
       x = "Condition", 
       y = "Mean Response Time (ms)") + 
  scale_fill_discrete(name="Speaker", labels = c("Multiple", "Single")) +
  geom_text(aes(label = round(reaction, digits = 2)),
            size = 3,
            position=position_dodge(width=0.9),
            vjust=-0.25) + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 8, colour = "black"),
        legend.position = c(0.9,0.9), 
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_text(size = 9),
        #legend.direction = "horizontal",
        legend.key.size = unit(4, "mm")) -> p.test.c.rt
```

## Contrast
```{r}
# Contrast ranking
## Filter, mutate to factor, and group by
dfByContrast.chance <- dfMaster.chance %>% 
  filter(!is.na(Contrast)) %>% 
  mutate(Contrast = factor(Contrast)) %>% 
  group_by(Contrast, pair_type) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time))

# Plot Accuracy
dfByContrast.chance %>% 
  filter(!Contrast %in% c(19,20,21)) %>%
  ggplot(aes(x = mean_correct, y = Contrast, fill = pair_type)) + 
  theme_gray() +
  scale_fill_brewer(palette = "Set2", name = "Type") +
  geom_bar(stat = "identity") + 
  scale_y_discrete(labels = c("*k-c", "k-t", "c-t", "θ-ç", "*x-ç", "x-θ",
                              "d-g", "*g-ɟ", "ɟ-d", "*ɣ-ʝ", "ʝ-ð", "ɣ-ð",
                              "θ-t", "ç-c", "k-x", "d-ð", "ɟ-ʝ", "g-ɣ")) +
  coord_cartesian(xlim = c(60,110)) +
  labs(title = "Mean Accuracy by Contrast",
       subtitle = "Excluding below chance",
       y = "Contrast", 
       x = "Mean Correct (%)") + 
  geom_text(aes(label = round(mean_correct, digits = 2)),
            hjust = -0.25,
            vjust = 0.3,
            size = 3) + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black"),
        #legend.position = c(0.94,0.88), 
        legend.background = element_rect(fill = "transparent"), 
        #legend.direction = "horizontal",
        legend.key.size = unit(4, "mm")) -> p.con.acc

# Plot Reaction Time
dfByContrast.chance %>% 
  filter(!Contrast %in% c(19,20,21)) %>%
  ggplot(aes(x = reaction, y = Contrast, fill = pair_type)) + 
  theme_gray() +
  scale_fill_brewer(palette = "Set2", name = "Type") +
  geom_bar(stat = "identity") + 
  scale_y_discrete(labels = c("*k-c", "k-t", "c-t", "θ-ç", "*x-ç", "x-θ",
                              "d-g", "*g-ɟ", "ɟ-d", "*ɣ-ʝ", "ʝ-ð", "ɣ-ð",
                              "θ-t", "ç-c", "k-x", "d-ð", "ɟ-ʝ", "g-ɣ")) +
  coord_cartesian(xlim = c(300,1000)) +
  labs(title = "Mean Response Time by Contrast",
       subtitle = "Excluding below chance",
       y = "Contrast",
       x = "Mean Response Time (ms)") + 
  geom_text(aes(label = round(reaction, digits = 2)),
            hjust = -0.25,
            vjust = 0.3,
            size = 3) +
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black"),
        #legend.position = c(0.94,0.88), 
        legend.background = element_rect(fill = "transparent"), 
        #legend.direction = "horizontal",
        legend.key.size = unit(4, "mm")) -> p.con.rt

```

### Consonant Type
```{r}
# Regrouping to see how the obstruent types (stop-stop, fric-fric, stop-fric) look
dfByObs.chance <- dfMaster.chance %>% 
  filter(!is.na(obs_type)) %>% 
  mutate(Contrast = factor(Contrast), obs_type = factor(obs_type)) %>% 
  group_by(Contrast, obs_type) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time))

dfByObs.chance %>% 
  #filter(!Contrast %in% c(19,20,21)) %>%
  ggplot(aes(x = mean_correct, y = Contrast, fill = obs_type)) + 
  theme_gray() +
  scale_fill_brewer(palette = "Set2", name = "Type") +
  geom_bar(stat = "identity") + 
  scale_y_discrete(labels = c("*k-c", "k-t", "c-t", "θ-ç", "*x-ç", "x-θ",
                              "d-g", "*g-ɟ", "ɟ-d", "*ɣ-ʝ", "ʝ-ð", "ɣ-ð",
                              "θ-t", "ç-c", "k-x", "d-ð", "ɟ-ʝ", "g-ɣ")) +
  coord_cartesian(xlim = c(60,110)) +
  labs(title = "Mean Accuracy by Obstruent Pairing",
       subtitle = "Excluding below chance",
       y = "Contrast", 
       x = "Mean Correct (%)") + 
  geom_text(aes(label = round(mean_correct, digits = 2)),
            hjust = -0.25,
            vjust = 0.3,
            size = 3) + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black"),
        #legend.position = c(0.94,0.88), 
        legend.background = element_rect(fill = "transparent"), 
        #legend.direction = "horizontal",
        legend.key.size = unit(4, "mm"))

dfMaster.chance %>% 
  filter(!is.na(obs_type)) %>% 
  mutate(obs_type = factor(obs_type)) %>% 
  group_by(obs_type) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time)) %>%
  ggplot(aes(x = mean_correct, y = obs_type, fill = obs_type)) +
  theme_gray() +
  scale_fill_brewer(palette = "Set2") +
  geom_bar(stat = "identity", show.legend = FALSE) +
  coord_cartesian(xlim = c(60,100)) +
  labs(title = "Mean Accuracy by Obstruent Pairing",
       subtitle = "Excluding below chance",
       y = "Obstruent Pairing", 
       x = "Mean Correct (%)") + 
  geom_text(aes(label = round(mean_correct, digits = 2)),
            hjust = -0.25,
            vjust = 0.3,
            size = 3) + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black"),
        #legend.position = c(0.94,0.88), 
        legend.background = element_rect(fill = "transparent"), 
        #legend.direction = "horizontal",
        legend.key.size = unit(4, "mm")) -> p.obs.acc

dfMaster.chance %>% 
  filter(!is.na(obs_type)) %>% 
  mutate(obs_type = factor(obs_type)) %>% 
  group_by(obs_type) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time)) %>%
  ggplot(aes(x = reaction, y = obs_type, fill = obs_type)) +
  theme_gray() +
  scale_fill_brewer(palette = "Set2") +
  geom_bar(stat = "identity", show.legend = FALSE) +
  coord_cartesian(xlim = c(300,800)) +
  labs(title = "Mean Response Time by Obstruent Pairing",
       subtitle = "Excluding below chance",
       y = "Obstruent Pairing", 
       x = "Mean Response Time (ms)") + 
  geom_text(aes(label = round(reaction, digits = 2)),
            hjust = -0.25,
            vjust = 0.3,
            size = 3) + 
  theme(plot.title = element_text(face = "bold", margin = margin(5,0,5,0), size = 12),
        plot.title.position = "plot",
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black"),
        #legend.position = c(0.94,0.88), 
        legend.background = element_rect(fill = "transparent"), 
        #legend.direction = "horizontal",
        legend.key.size = unit(4, "mm")) -> p.obs.rt
```


## Contrast Type
```{r}
# Regrouping to see pair type (Native, Foreign, Foreign-Native) by condition
dfByPairType.chance <- dfMaster.chance %>% 
  filter(Block==4) %>%
  mutate(pair_type = factor(pair_type)) %>% 
  group_by(pair_type, Condition) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time))

# Plot Accuracy
dfByPairType.chance %>% ggplot(aes(x = pair_type, y = mean_correct, fill = pair_type)) + 
  theme_bw() +
  scale_fill_brewer(palette = "Set2", name = "Type") +
  geom_bar(stat = "identity", show.legend = FALSE) + 
  coord_cartesian(ylim = c(50,110)) +
  labs(title = "Mean Accuracy by Contrast Type - Test Block",
       subtitle = "Excluding below chance",
       x = "Contrast Type",
       y = "Mean Correct (%)") + 
  theme(plot.title = element_text(face = "bold", margin = margin(10,0,10,0), size = 12),
        plot.subtitle = element_text(size = 8),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black")) +
  geom_text(aes(label = round(mean_correct, digits = 2)), 
            vjust = -0.25,
            size = 3) +
  facet_wrap(vars(dfByPairType.chance$Condition)) -> p.ctype.acc

# Plot Reaction Time
dfByPairType.chance %>% ggplot(aes(x = pair_type, y = reaction, fill = pair_type)) + 
  theme_bw() +
  scale_fill_brewer(palette = "Set2", name = "Type") +
  geom_bar(stat = "identity", show.legend = FALSE) + 
  coord_cartesian(ylim = c(300,1200)) +
  labs(title = "Mean Response Time by Contrast Type - Test Block",
       subtitle = "Excluding below chance",
       x = "Contrast Type",
       y = "Mean Response Time (ms)") + 
  theme(plot.title = element_text(face = "bold", margin = margin(10,0,10,0), size = 12),
        plot.subtitle = element_text(size = 8),
        #plot.title.position = "plot",
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 2),
        axis.text = element_text(size = 10, colour = "black")) +
  geom_text(aes(label = round(reaction, digits = 2)),
            vjust = -0.25,
            size = 3) +
  facet_wrap(vars(dfByPairType.chance$Condition)) -> p.ctype.rt
```

```{r}
# Saving the above plots
ggsave("plot_ctype_acc.png", p.ctype.acc, device = agg_png, width = 12,
       height = 14,
       units = "cm", res = 300, scaling = 0.8)

ggsave("plot_ctype_rt.png", p.ctype.rt, device = agg_png, width = 12,
       height = 14,
       units = "cm", res = 300, scaling = 0.8)
```


```{r}
dfByPairType.ch2 <- dfMaster.chance %>% 
  filter(Block==4) %>%
  mutate(pair_type = factor(pair_type)) %>% 
  group_by(pair_type) %>% 
  reframe(count = n(),
          total_correct = sum(as.numeric(correct==1)),
          mean_correct = mean(as.numeric(levels(correct))[correct]*100),
          reaction = mean(response_time))

dfByPairType.ch2 %>% ggplot(aes(x = pair_type, y = mean_correct, fill = pair_type)) + 
  theme_bw() +
  scale_fill_brewer(palette = "Set2", name = "Type") +
  geom_bar(stat = "identity", show.legend = FALSE) + 
  coord_fixed(ratio = 1/35, ylim = c(0,100)) +
  labs(title = "Mean Accuracy by Contrast Type",
       x = "Contrast Type",
       y = "Mean Correct (%)") + 
  theme(plot.title = element_text(face = "bold", margin = margin(10,0,10,0), size = 12),
        axis.title.x = element_text(vjust = 0.5),
        axis.title.y = element_text(vjust = 1),
        axis.text = element_text(size = 10, colour = "black")) +
  geom_text(aes(label = round(mean_correct, digits = 2)), vjust = -0.25) # -> p.ctype.acc
```


```{r}
# Creating a table because the chart wasn't worth using
dfByPairType.chance %>% 
  select(pair_type, Condition, mean_correct) %>%
  pivot_wider(names_from = "Condition", values_from = "mean_correct") %>%
  kbl() %>%
  kable_styling() %>%
  add_header_above(c(" " = 1, "Condition 1" = 3, "Condition 2" = 3, "Condition 3" = 1))

dfByPairType.chance %>% 
  select(pair_type, Condition, mean_correct) %>%
  pivot_wider(names_from = "pair_type", values_from = "mean_correct") %>%
  kbl(booktabs = T, digits = 2) %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(" " = 1, "Contrast Type" = 3)) %>%
  column_spec(2, background = "#66C2A5") %>%
  column_spec(3, background = "#FC8D62") %>%
  column_spec(4, background = "#8DA0CB")
```

# Models
Before we do the models we are going to redo some of the dataframes to make them easier to use for statistical models.
```{r}
# Filter out the time-out responses by finding response = none or response_time = 3000
dfMaster_mdls <- dfMasterRaw.chance %>% filter(response != "None", !Participant %in% c("FF05","FF10","FF20","FM01","FM06")) %>% select(-Condition)

## With Condition as a seven level factor combining Conditions and Dialect
dfMaster_mdls <- dfMaster_mdls %>% 
  mutate(Condition = case_when(grepl("1a_", experiment_file) ~ "1-Athens",
                               grepl("1b_", experiment_file) ~ "1-Thessaloniki",
                               grepl("1c_", experiment_file) ~ "1-Crete",
                               grepl("2a_", experiment_file) ~ "2-Athens",
                               grepl("2b_", experiment_file) ~ "2-Thessaloniki",
                               grepl("2c_", experiment_file) ~ "2-Crete",
                               TRUE ~ "3-All")
         )

# Convert the categorical variables to factors
dfMaster_mdls <- dfMaster_mdls %>%
  mutate(Dialect = factor(Dialect, labels = c("All", "Athens", "Thessaloniki", "Crete")),
         test_sp = factor(case_when(Block == 4 & test_sp == 0 ~ "Multiple",
                                    Block == 4 & test_sp == 1 ~ "Single",
                                    TRUE ~ NA)),
         Block = factor(Block),
         correct = factor(correct),
         Condition = factor(Condition)
         )

dfMaster_mdls <- dfMaster_mdls %>%
  mutate(pair_type = case_when(Contrast %in% c(2,7,19) ~ "Native",
                               Contrast %in% c(4,5,6,10,11,12,14,17,20) ~ "Foreign",
                               Contrast %in% c(1,3,8,9,13,15,16,18,21) ~ "For-Nat",
                               TRUE ~ NA),
         obs_type = case_when(Contrast %in% c(1,2,3,7,8,9) ~ "Stop-Stop",
                              Contrast %in% c(4,5,6,10,11,12) ~ "Fric-Fric",
                              Contrast %in% c(13,14,15,16,17,18) ~ "Stop-Fric",
                              TRUE ~ NA)
         )

dfLog.chance <- dfMaster_mdls %>% mutate(response_time = log(response_time))
```

# LMER
Creating multiple models by slowly adding fixed effects, random effects and slopes.

If you would like to save time, and your computer, load the all 12 models (lmer and glmer) from the perc_models.RData
```{r}
mdl1 <- dfLog.chance %>%
  filter(!is.infinite(response_time)) %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>% 
  #filter(!Contrast %in% c(19,20,21)) %>% 
  lmer(response_time ~ Condition + (1|Participant) + (Condition|Contrast), data = .,
       control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5))) 

mdl2 <- dfLog.chance %>%
  filter(!is.infinite(response_time)) %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>% 
  #filter(!Contrast %in% c(19,20,21)) %>% 
  lmer(response_time ~ Condition + (1|Participant) + (1|Contrast), data = .,
       control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5))) 

mdl3 <- dfLog.chance %>%
  filter(!is.infinite(response_time)) %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>% 
  #filter(!Contrast %in% c(19,20,21)) %>% 
  lmer(response_time ~ Condition + test_sp + (1|Participant) + (1|Contrast), data = .,
       control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5))) 

mdl4 <- dfLog.chance %>%
  filter(!is.infinite(response_time)) %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>% 
  #filter(!Contrast %in% c(19,20,21)) %>% 
  lmer(response_time ~ Condition + test_sp + (1|Participant) + (Condition|Contrast), data = .,
       control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5))) 

mdl5 <- dfLog.chance %>%
  filter(!is.infinite(response_time)) %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>% 
  #filter(!Contrast %in% c(19,20,21)) %>% 
  lmer(response_time ~ Condition + test_sp + (test_sp|Participant) + (Condition|Contrast), data = .,
       control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5)))

mdl6 <- dfLog.chance %>%
  filter(!is.infinite(response_time)) %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>% 
  #filter(!Contrast %in% c(19,20,21)) %>% 
  lmer(response_time ~ Condition * test_sp + (test_sp|Participant) + (Condition|Contrast), data = .,
       control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5))) 
```
## Anova
```{r}
# mdl1 and 2 have more observations because of the lack of test_sp
# The rest match and are essentially the same as if I had filtered for block 4
anova(mdl1, mdl2)
anova(mdl6, mdl5, mdl4, mdl3)
```
## Summary and Coefficients
```{r}
# Prefered of the single fixed effect models
summary(mdl1)
coef(mdl1)
```

```{r}
summary(mdl6)
coef(mdl6)
```

```{r}
# Create a table of the results
tidy(mdl6, effects = "fixed") %>% 
  select(-effect, -df) %>% 
  mutate(p.value = scales::pvalue(p.value)) %>%
  kbl(format = "latex", booktabs = T, 
      col.names = c("Predictor", "B", "SE", "t", "p"), 
      digits = c(0, 2, 3, 2, 3), 
      align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(full_width = T) %>% save_kable("lmer_fixed.tex", float = FALSE)
```

## Emmeans
### Model 1
```{r}
mdl1 %>% emmeans(pairwise ~ Condition)
```

```{r}
#emm_options(pbkrtest.limit = 10000)
emm_options(pbkrtest.limit = 5000)
```

### Model 6
```{r}
mdl6 %>% emmeans(pairwise ~ test_sp)
mdl6 %>% emmeans(pairwise ~ Condition)
mdl6 %>% emmeans(pairwise ~ Condition * test_sp)
```

# GLMER
```{r}
gl.mdl1 <- dfMaster_mdls %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>%
  #filter(!Contrast %in% c(19,20,21)) %>%
  glmer(correct ~ Condition + (1|Participant) + (1|Contrast), data = ., family = binomial)

gl.mdl2 <- dfMaster_mdls %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>%
  #filter(!Contrast %in% c(19,20,21)) %>%
  glmer(correct ~ Condition + (1|Participant) + (Condition|Contrast), data = ., family = binomial)

gl.mdl3 <- dfMaster_mdls %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>%
  #filter(!Contrast %in% c(19,20,21)) %>%
  glmer(correct ~ Condition + test_sp + (1|Participant) + (1|Contrast), data = ., family = binomial)

gl.mdl4 <- dfMaster_mdls %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>%
  #filter(!Contrast %in% c(19,20,21)) %>%
  glmer(correct ~ Condition + test_sp + (1|Participant) + (Condition|Contrast), data = ., family = binomial)

gl.mdl5 <- dfMaster_mdls %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>%
  #filter(!Contrast %in% c(19,20,21)) %>%
  glmer(correct ~ Condition + test_sp + (test_sp|Participant) + (Condition|Contrast), data = ., family = binomial)
```

```{r}
# Run this one separately becuase it takes ages
gl.mdl6 <- dfMaster_mdls %>%
  filter(Block != 0) %>%
  #filter(!is.na(Contrast)) %>%
  #filter(!Contrast %in% c(19,20,21)) %>%
  glmer(correct ~ Condition * test_sp + (test_sp|Participant) + (Condition|Contrast), data = ., family = binomial)
```
## Anova
```{r}
anova(gl.mdl1, gl.mdl2)
anova(gl.mdl3, gl.mdl4, gl.mdl5, gl.mdl6)
```
## Summary and Coefficients
```{r}
# Prefered of the single fixed effect
summary(gl.mdl2)
coef(gl.mdl2)
```

```{r}
summary(gl.mdl6)
coef(gl.mdl6)
```

```{r}
# Create table of the results
tidy(gl.mdl6, effects = "fixed") %>% 
  select(-effect) %>% 
  mutate(p.value = scales::pvalue(p.value)) %>%
  kbl(format = "latex", booktabs = T, 
      col.names = c("Predictor", "B", "SE", "t", "p"), 
      digits = c(0, 2, 3, 2, 3), 
      align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(full_width = T) %>% save_kable("glmer_fixed.tex", float = FALSE)
```

```{r}
tidy(gl.mdl2, effects = "fixed") %>%
  select(-effect) %>%
  mutate(p.value = scales::pvalue(p.value)) %>%
  kbl(digits = c(0, 2, 3, 2, 3),) %>% kable_styling(full_width = T)
```

## Emmeans
### Model 2
```{r}
gl.mdl2 %>% emmeans(pairwise ~ Condition, type = "response")
```

### Model 6
```{r}
gl.mdl6 %>% emmeans(pairwise ~ test_sp, type = "response")
gl.mdl6 %>% emmeans(pairwise ~ Condition, type = "response")
gl.mdl6 %>% emmeans(pairwise ~ Condition * test_sp, type = "response")
```